Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-07-19 src/tex/ms.tex
minor edits

A successful transit detection requires a sufficient signal-to-noise ratio, which is sensitive to the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for \plato\
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
In line with this requirement, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal~\citep[][Matuszewski et al., in prep.]{plato2017}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.

@@

\begin{acknowledgments}
We thank the anonymous referees for their constructive reports that helped to improve this manuscript.
The authors thank Gabriele Cugno, Yann Fabel, Brad Foley, Lisa Kaltenegger, Ravi Kopparapu, Eric Mamajek, Megan Mansfield, Paul Molliere, Gijs Mulders, Matthew Murphy, Sukrit Ranjan, and Terry-Ann Suer for insightful discussions.
We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
This material is based upon work supported by the National Aeronautics and Space Administration under Agreement No. 80NSSC21K0593 for the program ``Alien Earths''.
The results reported herein benefitted from collaborations and/or information exchange within NASA’s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA’s Science Mission Directorate.
This work has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia\ Multilateral Agreement.
T.L. was supported by a grant from the Branco Weiss Foundation.
G.B. acknowledges support from the NASA Astrophysics Data Analysis Program under Grant No.~80NSSC20K0446.
A.S. acknowledges support from NASA's Habitable Worlds Program (No.~80NSSC20K0226).
\end{acknowledgments}

>>>>

A successful transit detection requires a sufficient signal-to-noise ratio, which is sensitive to the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for \plato\
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
In line with this requirement, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal\rev{~\citep[][Matuszewski et al., subm.]{plato2017}}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.

@@

\begin{acknowledgments}
The authors thank Gabriele Cugno, Yann Fabel, Brad Foley, Lisa Kaltenegger, Ravi Kopparapu, Eric Mamajek, Megan Mansfield, Paul Molliere, Gijs Mulders, Matthew Murphy, Sukrit Ranjan, and Terry-Ann Suer for insightful discussions.
We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
We thank the anonymous referees for providing insightful reports that helped to improve this manuscript.
This material is based upon work supported by the National Aeronautics and Space Administration under Agreement No. 80NSSC21K0593 for the program ``Alien Earths''.
The results reported herein benefitted from collaborations and/or information exchange within NASA’s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA’s Science Mission Directorate.
This work has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia\ Multilateral Agreement.
T.L. was supported by a grant from the Branco Weiss Foundation.
G.B. acknowledges support from the NASA Astrophysics Data Analysis Program under Grant No.~80NSSC20K0446.
A.S. acknowledges support from NASA's Habitable Worlds Program (No.~80NSSC20K0226).
\end{acknowledgments}
